The Efficient Handling of Guards in the Design of RPython's Tracing JIT

### 2012-08-14 talk/vmil2012/paper.tex
cite Self debugging paper

Deutsch et. al.~\cite{deutsch_efficient_1984} describe the use of stack descriptions
to make it possible to do source-level debugging of JIT-compiled code.
Self uses deoptimization to reach the same goal~\cite{XXX}.
When a function is to be debugged, the optimized code version is left
and one compiled without inlining and other optimizations is entered.
Self uses scope descriptors to describe the frames
that need to be re-created when leaving the optimized code.
The scope descriptors are between 0.45 and 0.76 times
the size of the generated machine code.

>>>>

Deutsch et. al.~\cite{deutsch_efficient_1984} describe the use of stack descriptions
to make it possible to do source-level debugging of JIT-compiled code.
Self uses deoptimization to reach the same goal~\cite{holzle_debugging_1992}.
When a function is to be debugged, the optimized code version is left
and one compiled without inlining and other optimizations is entered.
Self uses scope descriptors to describe the frames
that need to be re-created when leaving the optimized code.
The scope descriptors are between 0.42 and 1.09 times
the size of the generated machine code.
All the information needed for debugging together
is between 1.22 and 2.33 times the size of generated machine code,
according to the paper.
